### 2014-10-06 LaTeX/mCapSimPlot.tex
updating plots

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:40:21
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,107.99) --
	( 61.80,109.63) --
	( 66.56,111.28) --
	( 71.31,112.93) --
	( 76.07,114.58) --
	( 80.82,116.22) --
	( 85.58,117.87) --
	( 90.34,119.52) --
	( 95.09,121.16) --
	( 99.85,122.81) --
	(104.60,124.46) --
	(109.36,126.11) --
	(114.11,127.75) --
	(118.87,129.40) --
	(123.63,131.05) --
	(128.38,132.70) --
	(133.14,134.34) --
	(137.89,135.99) --
	(142.65,137.64) --
	(147.40,139.28) --
	(152.16,140.93) --
	(156.92,142.58) --
	(161.67,144.23) --
	(166.43,145.87) --
	(171.18,147.52) --
	(175.94,149.17) --
	(180.70,150.81) --
	(185.45,152.46) --
	(190.21,154.11) --
	(194.96,155.76) --
	(199.72,157.40) --
	(204.47,159.05) --
	(209.23,160.70) --
	(213.99,162.34) --
	(218.74,163.99) --
	(223.50,165.64) --
	(228.25,167.29) --
	(233.01,168.93) --
	(237.76,170.58) --
	(242.52,172.23) --
	(247.28,173.88) --
	(252.03,175.52) --
	(256.79,177.17) --
	(261.54,178.82) --
	(266.30,180.46) --
	(271.05,182.11) --
	(275.81,183.76) --
	(280.57,185.41) --
	(285.32,187.05) --
	(290.08,188.70) --
	(294.83,190.35) --
	(299.59,191.99) --
	(304.35,193.64) --
	(309.10,195.29) --
	(313.86,196.94) --
	(318.61,198.58) --
	(323.37,200.23) --
	(328.12,201.88) --
	(332.88,203.52) --
	(337.64,205.17) --
	(342.39,206.82) --
	(347.15,208.47) --
	(351.90,210.11) --
	(356.66,211.76) --
	(361.41,213.41) --
	(366.17,215.05) --
	(370.93,216.70) --
	(375.68,218.35) --
	(380.44,220.00) --
	(385.19,221.64) --
	(389.95,223.29) --
	(394.70,224.94) --
	(399.46,226.59) --
	(404.22,228.23);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,170.30) --
	( 61.80,170.75) --
	( 66.56,171.43) --
	( 71.31,172.00) --
	( 76.07,172.73) --
	( 80.82,173.39) --
	( 85.58,174.13) --
	( 90.34,174.65) --
	( 95.09,175.20) --
	( 99.85,175.83) --
	(104.60,176.50) --
	(109.36,177.16) --
	(114.11,177.80) --
	(118.87,178.59) --
	(123.63,179.29) --
	(128.38,179.81) --
	(133.14,180.41) --
	(137.89,181.20) --
	(142.65,181.89) --
	(147.40,182.78) --
	(152.16,183.41) --
	(156.92,183.93) --
	(161.67,184.69) --
	(166.43,185.42) --
	(171.18,186.20) --
	(175.94,187.05) --
	(180.70,188.02) --
	(185.45,188.60) --
	(190.21,189.50) --
	(194.96,190.46) --
	(199.72,191.24) --
	(204.47,192.15) --
	(209.23,193.07) --
	(213.99,194.11) --
	(218.74,195.08) --
	(223.50,196.00) --
	(228.25,196.95) --
	(233.01,198.08) --
	(237.76,199.37) --
	(242.52,200.49) --
	(247.28,201.79) --
	(252.03,203.07) --
	(256.79,204.30) --
	(261.54,205.54) --
	(266.30,207.04) --
	(271.05,208.33) --
	(275.81,209.80) --
	(280.57,211.29) --
	(285.32,212.83) --
	(290.08,214.53) --
	(294.83,216.23) --
	(299.59,217.85) --
	(304.35,219.60) --
	(309.10,221.58) --
	(313.86,223.41) --
	(318.61,225.32) --
	(323.37,227.31) --
	(328.12,229.50) --
	(332.88,231.70) --
	(337.64,233.85) --
	(342.39,235.89) --
	(347.15,238.03) --
	(351.90,240.17) --
	(356.66,242.38) --
	(361.41,244.58) --
	(366.17,246.95) --
	(370.93,249.06) --
	(375.68,251.34) --
	(380.44,253.72) --
	(385.19,255.97) --
	(389.95,258.60) --
	(394.70,261.10) --
	(399.46,263.65) --
	(404.22,265.99) --
	(404.22,189.23) --
	(399.46,188.51) --
	(394.70,187.90) --
	(389.95,187.02) --
	(385.19,186.13) --
	(380.44,185.09) --
	(375.68,184.39) --
	(370.93,183.61) --
	(366.17,182.69) --
	(361.41,181.83) --
	(356.66,180.81) --
	(351.90,179.77) --
	(347.15,178.57) --
	(342.39,177.44) --
	(337.64,176.32) --
	(332.88,175.29) --
	(328.12,174.08) --
	(323.37,172.90) --
	(318.61,171.57) --
	(313.86,170.24) --
	(309.10,168.76) --
	(304.35,167.31) --
	(299.59,165.82) --
	(294.83,164.52) --
	(290.08,162.91) --
	(285.32,161.16) --
	(280.57,159.46) --
	(275.81,157.79) --
	(271.05,155.95) --
	(266.30,154.07) --
	(261.54,152.24) --
	(256.79,150.23) --
	(252.03,148.25) --
	(247.28,146.22) --
	(242.52,143.99) --
	(237.76,141.83) --
	(233.01,139.84) --
	(228.25,137.63) --
	(223.50,135.49) --
	(218.74,133.10) --
	(213.99,130.62) --
	(209.23,128.31) --
	(204.47,125.87) --
	(199.72,123.59) --
	(194.96,121.22) --
	(190.21,118.75) --
	(185.45,116.43) --
	(180.70,114.03) --
	(175.94,111.47) --
	(171.18,108.99) --
	(166.43,106.38) --
	(161.67,103.74) --
	(156.92,101.22) --
	(152.16, 98.74) --
	(147.40, 96.24) --
	(142.65, 93.73) --
	(137.89, 91.21) --
	(133.14, 88.50) --
	(128.38, 85.77) --
	(123.63, 83.16) --
	(118.87, 80.48) --
	(114.11, 77.79) --
	(109.36, 75.08) --
	(104.60, 72.30) --
	( 99.85, 69.52) --
	( 95.09, 66.86) --
	( 90.34, 64.14) --
	( 85.58, 61.43) --
	( 80.82, 58.71) --
	( 76.07, 55.94) --
	( 71.31, 53.21) --
	( 66.56, 50.50) --
	( 61.80, 47.80) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,159.56) --
	( 61.80,160.25) --
	( 66.56,160.98) --
	( 71.31,161.86) --
	( 76.07,162.52) --
	( 80.82,163.37) --
	( 85.58,164.21) --
	( 90.34,164.90) --
	( 95.09,165.74) --
	( 99.85,166.75) --
	(104.60,167.59) --
	(109.36,168.46) --
	(114.11,169.19) --
	(118.87,170.16) --
	(123.63,170.99) --
	(128.38,171.84) --
	(133.14,172.69) --
	(137.89,173.59) --
	(142.65,174.41) --
	(147.40,175.17) --
	(152.16,176.19) --
	(156.92,177.17) --
	(161.67,178.09) --
	(166.43,178.94) --
	(171.18,179.97) --
	(175.94,180.98) --
	(180.70,181.99) --
	(185.45,182.96) --
	(190.21,183.82) --
	(194.96,184.88) --
	(199.72,185.88) --
	(204.47,186.83) --
	(209.23,187.76) --
	(213.99,188.99) --
	(218.74,190.13) --
	(223.50,191.26) --
	(228.25,192.31) --
	(233.01,193.53) --
	(237.76,194.62) --
	(242.52,195.84) --
	(247.28,197.18) --
	(252.03,198.48) --
	(256.79,199.68) --
	(261.54,201.07) --
	(266.30,202.56) --
	(271.05,204.06) --
	(275.81,205.62) --
	(280.57,207.24) --
	(285.32,209.00) --
	(290.08,210.51) --
	(294.83,212.14) --
	(299.59,213.87) --
	(304.35,215.72) --
	(309.10,217.52) --
	(313.86,219.34) --
	(318.61,221.26) --
	(323.37,223.16) --
	(328.12,225.10) --
	(332.88,227.06) --
	(337.64,228.96) --
	(342.39,231.01) --
	(347.15,233.07) --
	(351.90,235.12) --
	(356.66,237.31) --
	(361.41,239.43) --
	(366.17,241.62) --
	(370.93,243.83) --
	(375.68,246.04) --
	(380.44,248.34) --
	(385.19,250.61) --
	(389.95,252.92) --
	(394.70,255.34) --
	(399.46,257.65) --
	(404.22,260.08) --
	(404.22,196.18) --
	(399.46,195.16) --
	(394.70,194.11) --
	(389.95,193.22) --
	(385.19,192.29) --
	(380.44,191.22) --
	(375.68,190.29) --
	(370.93,189.27) --
	(366.17,188.31) --
	(361.41,187.21) --
	(356.66,185.94) --
	(351.90,184.86) --
	(347.15,183.77) --
	(342.39,182.69) --
	(337.64,181.59) --
	(332.88,180.34) --
	(328.12,179.09) --
	(323.37,177.75) --
	(318.61,176.29) --
	(313.86,174.79) --
	(309.10,173.33) --
	(304.35,171.86) --
	(299.59,170.35) --
	(294.83,168.77) --
	(290.08,167.23) --
	(285.32,165.59) --
	(280.57,163.88) --
	(275.81,162.14) --
	(271.05,160.29) --
	(266.30,158.47) --
	(261.54,156.48) --
	(256.79,154.63) --
	(252.03,152.76) --
	(247.28,150.64) --
	(242.52,148.69) --
	(237.76,146.57) --
	(233.01,144.54) --
	(228.25,142.40) --
	(223.50,140.17) --
	(218.74,137.98) --
	(213.99,135.99) --
	(209.23,133.82) --
	(204.47,131.54) --
	(199.72,129.37) --
	(194.96,127.03) --
	(190.21,124.77) --
	(185.45,122.49) --
	(180.70,120.16) --
	(175.94,117.80) --
	(171.18,115.40) --
	(166.43,113.13) --
	(161.67,110.68) --
	(156.92,108.42) --
	(152.16,105.89) --
	(147.40,103.39) --
	(142.65,100.83) --
	(137.89, 98.32) --
	(133.14, 95.77) --
	(128.38, 93.33) --
	(123.63, 90.81) --
	(118.87, 88.34) --
	(114.11, 85.90) --
	(109.36, 83.33) --
	(104.60, 80.84) --
	( 99.85, 78.40) --
	( 95.09, 75.83) --
	( 90.34, 73.27) --
	( 85.58, 70.75) --
	( 80.82, 68.24) --
	( 76.07, 65.78) --
	( 71.31, 63.28) --
	( 66.56, 60.67) --
	( 61.80, 58.16) --
	( 57.05, 55.65) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,101.49) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,183.81) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,266.13) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 41.46, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 89.02, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.58, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (184.13, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.69, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (279.25, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.81, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (374.36, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

>>>>

% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:45
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.62) --
	( 60.61,108.24) --
	( 64.85,109.70) --
	( 64.98,109.74) --
	( 78.30,114.31) --
	( 86.71,117.20) --
	( 92.34,119.13) --
	( 95.59,120.24) --
	(101.92,122.42) --
	(110.88,125.49) --
	(154.64,140.51) --
	(158.01,141.66) --
	(171.43,146.26) --
	(178.49,148.69) --
	(187.92,151.92) --
	(192.71,153.57) --
	(195.62,154.56) --
	(195.71,154.59) --
	(196.35,154.81) --
	(198.04,155.39) --
	(199.87,156.02) --
	(204.99,157.78) --
	(205.19,157.85) --
	(209.65,159.38) --
	(211.50,160.01) --
	(215.87,161.51) --
	(217.33,162.01) --
	(217.43,162.05) --
	(217.68,162.13) --
	(218.17,162.30) --
	(220.17,162.99) --
	(220.33,163.04) --
	(220.93,163.25) --
	(221.63,163.49) --
	(222.58,163.81) --
	(223.29,164.06) --
	(223.54,164.14) --
	(223.59,164.16) --
	(224.00,164.30) --
	(229.14,166.07) --
	(231.15,166.76) --
	(231.34,166.82) --
	(232.39,167.18) --
	(233.34,167.51) --
	(234.25,167.82) --
	(235.24,168.16) --
	(236.22,168.49) --
	(237.40,168.90) --
	(237.41,168.90) --
	(239.29,169.55) --
	(239.31,169.55) --
	(240.03,169.80) --
	(240.80,170.06) --
	(241.27,170.23) --
	(241.65,170.36) --
	(242.95,170.80) --
	(244.78,171.43) --
	(248.30,172.64) --
	(249.74,173.13) --
	(250.22,173.30) --
	(250.38,173.35) --
	(250.69,173.46) --
	(251.97,173.90) --
	(252.46,174.07) --
	(253.69,174.49) --
	(253.89,174.55) --
	(254.34,174.71) --
	(255.74,175.19) --
	(256.94,175.60) --
	(258.99,176.31) --
	(260.08,176.68) --
	(260.16,176.71) --
	(261.39,177.13) --
	(262.57,177.53) --
	(263.47,177.84) --
	(264.14,178.07) --
	(264.43,178.17) --
	(264.94,178.35) --
	(265.11,178.40) --
	(265.48,178.53) --
	(265.54,178.55) --
	(266.69,178.95) --
	(266.70,178.95) --
	(267.74,179.31) --
	(267.83,179.34) --
	(267.95,179.38) --
	(268.15,179.45) --
	(268.32,179.51) --
	(268.51,179.57) --
	(268.75,179.66) --
	(269.12,179.78) --
	(269.30,179.84) --
	(269.75,180.00) --
	(269.91,180.05) --
	(271.51,180.60) --
	(272.31,180.88) --
	(272.40,180.91) --
	(272.91,181.08) --
	(273.01,181.11) --
	(273.29,181.21) --
	(273.48,181.28) --
	(274.31,181.56) --
	(274.85,181.75) --
	(274.88,181.76) --
	(275.50,181.97) --
	(276.03,182.15) --
	(276.14,182.19) --
	(276.73,182.39) --
	(276.77,182.41) --
	(277.28,182.58) --
	(277.37,182.61) --
	(278.83,183.11) --
	(278.93,183.15) --
	(278.99,183.17) --
	(279.03,183.18) --
	(279.36,183.30) --
	(279.83,183.46) --
	(279.90,183.48) --
	(280.21,183.59) --
	(280.36,183.64) --
	(280.41,183.66) --
	(280.47,183.68) --
	(280.50,183.68) --
	(280.60,183.72) --
	(280.63,183.73) --
	(281.16,183.91) --
	(281.52,184.03) --
	(281.60,184.06) --
	(283.10,184.58) --
	(283.28,184.64) --
	(283.34,184.66) --
	(283.74,184.80) --
	(283.80,184.82) --
	(284.26,184.97) --
	(284.43,185.03) --
	(284.75,185.14) --
	(284.80,185.16) --
	(284.81,185.16) --
	(284.81,185.16) --
	(284.84,185.18) --
	(284.88,185.19) --
	(285.44,185.38) --
	(285.67,185.46) --
	(286.04,185.59) --
	(286.70,185.81) --
	(286.95,185.90) --
	(287.76,186.18) --
	(288.16,186.31) --
	(288.45,186.41) --
	(288.86,186.55) --
	(289.03,186.61) --
	(289.13,186.65) --
	(289.30,186.70) --
	(289.61,186.81) --
	(289.71,186.85) --
	(289.99,186.94) --
	(290.44,187.10) --
	(291.29,187.39) --
	(291.45,187.44) --
	(291.58,187.49) --
	(292.20,187.70) --
	(292.36,187.75) --
	(292.77,187.89) --
	(292.78,187.90) --
	(292.85,187.92) --
	(292.94,187.95) --
	(293.49,188.14) --
	(293.61,188.18) --
	(293.90,188.28) --
	(293.94,188.30) --
	(295.12,188.70) --
	(295.85,188.95) --
	(296.61,189.21) --
	(297.11,189.38) --
	(297.99,189.68) --
	(298.09,189.72) --
	(298.13,189.74) --
	(298.21,189.76) --
	(298.45,189.84) --
	(298.48,189.85) --
	(298.71,189.93) --
	(298.89,190.00) --
	(299.22,190.11) --
	(300.07,190.40) --
	(300.69,190.61) --
	(301.34,190.83) --
	(301.81,191.00) --
	(301.86,191.01) --
	(302.06,191.08) --
	(302.08,191.09) --
	(302.20,191.13) --
	(302.30,191.16) --
	(302.45,191.22) --
	(302.52,191.24) --
	(302.61,191.27) --
	(302.89,191.37) --
	(302.93,191.38) --
	(303.17,191.46) --
	(304.10,191.78) --
	(304.31,191.85) --
	(304.47,191.91) --
	(304.48,191.91) --
	(304.60,191.95) --
	(304.68,191.98) --
	(305.11,192.13) --
	(305.28,192.19) --
	(305.76,192.35) --
	(305.86,192.39) --
	(306.15,192.49) --
	(307.03,192.79) --
	(307.16,192.83) --
	(307.37,192.90) --
	(308.42,193.27) --
	(308.63,193.34) --
	(308.79,193.39) --
	(309.08,193.49) --
	(309.55,193.65) --
	(309.72,193.71) --
	(310.36,193.93) --
	(310.45,193.96) --
	(310.80,194.08) --
	(310.98,194.14) --
	(311.09,194.18) --
	(311.49,194.32) --
	(311.71,194.39) --
	(311.87,194.45) --
	(312.39,194.63) --
	(312.68,194.73) --
	(312.75,194.75) --
	(314.09,195.21) --
	(314.12,195.22) --
	(314.55,195.37) --
	(314.84,195.47) --
	(315.05,195.54) --
	(315.28,195.62) --
	(315.54,195.71) --
	(315.61,195.73) --
	(315.65,195.75) --
	(316.29,195.97) --
	(316.37,195.99) --
	(316.58,196.06) --
	(316.61,196.07) --
	(316.72,196.11) --
	(317.13,196.25) --
	(318.60,196.76) --
	(319.14,196.94) --
	(320.71,197.48) --
	(321.34,197.70) --
	(321.47,197.74) --
	(322.56,198.12) --
	(322.64,198.14) --
	(322.93,198.24) --
	(323.98,198.60) --
	(324.06,198.63) --
	(324.53,198.79) --
	(324.82,198.89) --
	(325.46,199.11) --
	(325.85,199.24) --
	(325.87,199.25) --
	(325.91,199.27) --
	(326.16,199.35) --
	(326.46,199.45) --
	(327.01,199.64) --
	(327.50,199.81) --
	(327.78,199.91) --
	(328.37,200.11) --
	(328.92,200.30) --
	(330.17,200.73) --
	(330.38,200.80) --
	(330.88,200.97) --
	(333.53,201.88) --
	(333.56,201.89) --
	(333.69,201.94) --
	(333.82,201.98) --
	(333.83,201.98) --
	(335.38,202.51) --
	(335.47,202.55) --
	(337.65,203.29) --
	(338.50,203.58) --
	(338.83,203.70) --
	(338.87,203.71) --
	(339.04,203.77) --
	(339.21,203.83) --
	(339.40,203.89) --
	(339.55,203.94) --
	(339.76,204.02) --
	(339.84,204.04) --
	(340.15,204.15) --
	(340.28,204.20) --
	(340.65,204.32) --
	(341.52,204.62) --
	(342.53,204.97) --
	(343.79,205.40) --
	(343.95,205.45) --
	(345.11,205.85) --
	(345.20,205.89) --
	(345.78,206.08) --
	(346.49,206.33) --
	(346.80,206.43) --
	(346.94,206.48) --
	(347.30,206.60) --
	(348.63,207.06) --
	(348.84,207.13) --
	(349.59,207.39) --
	(350.01,207.53) --
	(350.27,207.62) --
	(350.57,207.73) --
	(351.61,208.08) --
	(352.50,208.39) --
	(354.60,209.11) --
	(354.77,209.17) --
	(355.03,209.26) --
	(355.06,209.27) --
	(355.38,209.38) --
	(355.44,209.40) --
	(355.66,209.47) --
	(355.69,209.48) --
	(356.06,209.61) --
	(356.08,209.62) --
	(356.57,209.78) --
	(356.86,209.88) --
	(356.99,209.93) --
	(357.04,209.94) --
	(357.10,209.97) --
	(357.28,210.03) --
	(357.68,210.17) --
	(357.71,210.18) --
	(358.36,210.40) --
	(358.45,210.43) --
	(358.80,210.55) --
	(359.58,210.82) --
	(360.14,211.01) --
	(360.17,211.02) --
	(360.28,211.06) --
	(360.68,211.20) --
	(362.54,211.83) --
	(362.92,211.96) --
	(362.99,211.99) --
	(362.99,211.99) --
	(363.68,212.22) --
	(363.71,212.23) --
	(364.25,212.42) --
	(364.57,212.53) --
	(364.77,212.60) --
	(365.00,212.68) --
	(365.26,212.76) --
	(365.84,212.96) --
	(365.84,212.96) --
	(365.92,212.99) --
	(366.04,213.03) --
	(366.47,213.18) --
	(367.05,213.38) --
	(368.20,213.78) --
	(368.39,213.84) --
	(368.50,213.88) --
	(370.21,214.46) --
	(371.17,214.79) --
	(371.58,214.94) --
	(372.02,215.09) --
	(373.58,215.62) --
	(376.96,216.78) --
	(378.52,217.32) --
	(383.85,219.15) --
	(384.44,219.35) --
	(384.92,219.51) --
	(385.30,219.64) --
	(385.73,219.79) --
	(385.96,219.87) --
	(386.70,220.12) --
	(386.81,220.16) --
	(387.17,220.28) --
	(387.19,220.29) --
	(387.24,220.31) --
	(387.39,220.36) --
	(387.67,220.46) --
	(388.26,220.66) --
	(389.16,220.97) --
	(389.82,221.19) --
	(390.40,221.39) --
	(390.44,221.41) --
	(390.79,221.53) --
	(391.07,221.62) --
	(395.16,223.02) --
	(396.00,223.31) --
	(396.15,223.37) --
	(403.52,225.89) --
	(404.02,226.07);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.20) --
	( 60.61,166.06) --
	( 64.85,166.50) --
	( 64.98,166.52) --
	( 78.30,168.34) --
	( 86.71,169.62) --
	( 92.34,170.49) --
	( 95.59,171.09) --
	(101.92,171.91) --
	(110.88,173.03) --
	(154.64,179.87) --
	(158.01,180.61) --
	(171.43,182.79) --
	(178.49,184.14) --
	(187.92,186.16) --
	(192.71,186.96) --
	(195.62,187.49) --
	(195.71,187.52) --
	(196.35,187.67) --
	(198.04,187.95) --
	(199.87,188.32) --
	(204.99,189.26) --
	(205.19,189.29) --
	(209.65,190.35) --
	(211.50,190.74) --
	(215.87,191.88) --
	(217.33,192.18) --
	(217.43,192.18) --
	(217.68,192.24) --
	(218.17,192.39) --
	(220.17,192.85) --
	(220.33,192.86) --
	(220.93,193.03) --
	(221.63,193.24) --
	(222.58,193.40) --
	(223.29,193.54) --
	(223.54,193.60) --
	(223.59,193.62) --
	(224.00,193.67) --
	(229.14,194.98) --
	(231.15,195.48) --
	(231.34,195.52) --
	(232.39,195.71) --
	(233.34,195.91) --
	(234.25,196.12) --
	(235.24,196.41) --
	(236.22,196.59) --
	(237.40,196.88) --
	(237.41,196.88) --
	(239.29,197.35) --
	(239.31,197.35) --
	(240.03,197.54) --
	(240.80,197.71) --
	(241.27,197.83) --
	(241.65,197.94) --
	(242.95,198.33) --
	(244.78,198.83) --
	(248.30,199.74) --
	(249.74,200.06) --
	(250.22,200.25) --
	(250.38,200.30) --
	(250.69,200.38) --
	(251.97,200.79) --
	(252.46,200.89) --
	(253.69,201.25) --
	(253.89,201.30) --
	(254.34,201.47) --
	(255.74,201.84) --
	(256.94,202.18) --
	(258.99,202.81) --
	(260.08,203.21) --
	(260.16,203.23) --
	(261.39,203.62) --
	(262.57,204.01) --
	(263.47,204.17) --
	(264.14,204.36) --
	(264.43,204.44) --
	(264.94,204.64) --
	(265.11,204.71) --
	(265.48,204.84) --
	(265.54,204.86) --
	(266.69,205.27) --
	(266.70,205.27) --
	(267.74,205.67) --
	(267.83,205.69) --
	(267.95,205.73) --
	(268.15,205.80) --
	(268.32,205.86) --
	(268.51,205.91) --
	(268.75,206.03) --
	(269.12,206.13) --
	(269.30,206.19) --
	(269.75,206.29) --
	(269.91,206.34) --
	(271.51,206.93) --
	(272.31,207.26) --
	(272.40,207.29) --
	(272.91,207.46) --
	(273.01,207.49) --
	(273.29,207.60) --
	(273.48,207.63) --
	(274.31,207.88) --
	(274.85,208.05) --
	(274.88,208.05) --
	(275.50,208.31) --
	(276.03,208.51) --
	(276.14,208.54) --
	(276.73,208.71) --
	(276.77,208.72) --
	(277.28,208.92) --
	(277.37,208.95) --
	(278.83,209.44) --
	(278.93,209.48) --
	(278.99,209.50) --
	(279.03,209.51) --
	(279.36,209.57) --
	(279.83,209.71) --
	(279.90,209.72) --
	(280.21,209.80) --
	(280.36,209.87) --
	(280.41,209.89) --
	(280.47,209.91) --
	(280.50,209.92) --
	(280.60,209.95) --
	(280.63,209.96) --
	(281.16,210.14) --
	(281.52,210.28) --
	(281.60,210.32) --
	(283.10,210.87) --
	(283.28,210.96) --
	(283.34,210.98) --
	(283.74,211.11) --
	(283.80,211.13) --
	(284.26,211.28) --
	(284.43,211.32) --
	(284.75,211.44) --
	(284.80,211.46) --
	(284.81,211.46) --
	(284.81,211.46) --
	(284.84,211.48) --
	(284.88,211.49) --
	(285.44,211.69) --
	(285.67,211.76) --
	(286.04,211.88) --
	(286.70,212.11) --
	(286.95,212.19) --
	(287.76,212.60) --
	(288.16,212.75) --
	(288.45,212.88) --
	(288.86,212.98) --
	(289.03,213.01) --
	(289.13,213.03) --
	(289.30,213.12) --
	(289.61,213.30) --
	(289.71,213.32) --
	(289.99,213.40) --
	(290.44,213.53) --
	(291.29,213.87) --
	(291.45,213.92) --
	(291.58,213.96) --
	(292.20,214.19) --
	(292.36,214.26) --
	(292.77,214.38) --
	(292.78,214.39) --
	(292.85,214.43) --
	(292.94,214.45) --
	(293.49,214.66) --
	(293.61,214.72) --
	(293.90,214.85) --
	(293.94,214.86) --
	(295.12,215.33) --
	(295.85,215.63) --
	(296.61,215.90) --
	(297.11,216.10) --
	(297.99,216.47) --
	(298.09,216.52) --
	(298.13,216.53) --
	(298.21,216.57) --
	(298.45,216.67) --
	(298.48,216.68) --
	(298.71,216.78) --
	(298.89,216.86) --
	(299.22,217.00) --
	(300.07,217.37) --
	(300.69,217.67) --
	(301.34,217.95) --
	(301.81,218.15) --
	(301.86,218.17) --
	(302.06,218.25) --
	(302.08,218.25) --
	(302.20,218.30) --
	(302.30,218.33) --
	(302.45,218.39) --
	(302.52,218.41) --
	(302.61,218.44) --
	(302.89,218.54) --
	(302.93,218.56) --
	(303.17,218.62) --
	(304.10,218.98) --
	(304.31,219.07) --
	(304.47,219.12) --
	(304.48,219.12) --
	(304.60,219.15) --
	(304.68,219.18) --
	(305.11,219.34) --
	(305.28,219.40) --
	(305.76,219.62) --
	(305.86,219.66) --
	(306.15,219.79) --
	(307.03,220.15) --
	(307.16,220.21) --
	(307.37,220.28) --
	(308.42,220.71) --
	(308.63,220.77) --
	(308.79,220.81) --
	(309.08,220.91) --
	(309.55,221.07) --
	(309.72,221.11) --
	(310.36,221.34) --
	(310.45,221.38) --
	(310.80,221.53) --
	(310.98,221.58) --
	(311.09,221.61) --
	(311.49,221.78) --
	(311.71,221.89) --
	(311.87,221.97) --
	(312.39,222.22) --
	(312.68,222.34) --
	(312.75,222.36) --
	(314.09,222.97) --
	(314.12,222.98) --
	(314.55,223.10) --
	(314.84,223.21) --
	(315.05,223.29) --
	(315.28,223.38) --
	(315.54,223.48) --
	(315.61,223.51) --
	(315.65,223.53) --
	(316.29,223.77) --
	(316.37,223.80) --
	(316.58,223.88) --
	(316.61,223.90) --
	(316.72,223.94) --
	(317.13,224.10) --
	(318.60,224.77) --
	(319.14,224.99) --
	(320.71,225.74) --
	(321.34,226.00) --
	(321.47,226.05) --
	(322.56,226.60) --
	(322.64,226.65) --
	(322.93,226.81) --
	(323.98,227.18) --
	(324.06,227.23) --
	(324.53,227.46) --
	(324.82,227.58) --
	(325.46,227.82) --
	(325.85,227.92) --
	(325.87,227.93) --
	(325.91,227.95) --
	(326.16,228.06) --
	(326.46,228.20) --
	(327.01,228.46) --
	(327.50,228.65) --
	(327.78,228.76) --
	(328.37,229.01) --
	(328.92,229.25) --
	(330.17,229.78) --
	(330.38,229.89) --
	(330.88,230.12) --
	(333.53,231.30) --
	(333.56,231.31) --
	(333.69,231.37) --
	(333.82,231.43) --
	(333.83,231.43) --
	(335.38,232.11) --
	(335.47,232.16) --
	(337.65,233.11) --
	(338.50,233.49) --
	(338.83,233.64) --
	(338.87,233.66) --
	(339.04,233.73) --
